An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
lots of sec 4 / app D changes

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
\end{definition}

@@

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{lemma}\label{lem:intersection-property-embedding}
  % Let polyhedral loss $L$ embed some discrete loss $\ell$.
  Let $\U'\subseteq\U$.  Then $\cap_{U\in\U'} U \neq \emptyset$ implies $\cap_{U\in\U'} R_u \neq \emptyset$.
\end{lemma}
\noindent
Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
(The statement of Lemma~\ref{lem:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points, and $\epsilon$-separated.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc$; and given an $\epsilon > 0$ and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  Define $\U = \{\Gamma(p) : p \in \simplex\}$.
  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \Sc : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}
In \S~\ref{sec:poly-ie-consistency} we generalize this construction beyond embeddings, where we only require that $L$ indirectly elicits $\prop\ell$.
There we will see that, perhaps surprisingly, this construction recovers every possible calibrated link.

@@

We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
In particular, fast convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  \label{thm:linear-regret-bound}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
\end{theorem}
In the proof (Appendix~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
This expression gives the intuition that larger link separation is generally better for performance.
In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
\raf{Updated the above; worth a check!}\jessie{Looks good to me?}

@@

\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
  Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.
  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
  For all $U \in \U$, define $R_U := \{r \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\R}$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}

\begin{proposition}\label{prop:link-converse}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \Sc : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \{r \in \Sc : r \in \gamma(p)\} = \gamma(p) \cap \Sc$.
  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \left(\gamma(p) \cap \Sc\right) = \Psi(u)$.
\bo{There is one problem here. For points that are not within $\epsilon$ of any optimal set, can a separated link map them to $\R \setminus \Sc$? If so, we need to slightly modify the argument.}
%\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower. Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
\end{proof}

\begin{corollary}
  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
\end{corollary}

@@

\section{Existence of a Separated Link} \label{app:sep-link-exists}
In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}.

We define some notation and assumptions to be used throughout this section.
Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
Finally, let the ``thickening'' $B(T,\epsilon)$ be defined as
  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]

\begin{assumption} \label{assume:cal}
  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
  The embedding points are $\{\varphi(r) : r \in \R\}$.
\end{assumption}

Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.

The next lemma shows that if a subset of $\U$ intersect, then their corresponding report sets intersect as well.
\begin{lemma} \label{lem:calibrated-pos}
  Let $\U' \subseteq \U$.
  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Let $u \in \cap_{U\in\U'} U$.
  Our first claim is that there exists $r$ such that $\Gamma_u \subseteq \gamma_r$.
  This follows from Proposition \ref{prop:embed-trim}, which shows that $\trim(\Gamma) = \{ \gamma_r : r \in \R\}$.
  Each $\Gamma_u$ is either in $\trim(\Gamma)$ or is contained in some set in $\trim(\Gamma)$, by definition, proving the first claim.
  Our second claim is that $r \in \cap_{U\in\U'} R_U$, which proves the lemma.
  To prove the second claim, take any $U \in \U'$.
  There is some $p$ such that $U = \Gamma(p)$, and we have in particular $p \in \Gamma_u$.
  By the first claim, $p \in \gamma_r$.
  By definition of embedding, $p \in \gamma_r \implies \varphi(r) \in \Gamma(p) = U$, so $r \in R_U$.
\end{proof}
Lemma \ref{lem:calibrated-pos} implies that there exists a $\psi$ such that $(L,\psi)$ indirectly elicits $\ell$: for each $u$, let $\U' = \{U\in\U : u \in U\}$ be the optimal sets that contain it; choose $r$ from the nonempty set $\cap_{U \in\U'} R_U$; and set $\psi(u) = r$.

\raf{ALTERNATIVE...}

Let $\gamma = \prop\ell$.
For all $U \in \U$, let $R_U = \{r: \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U = \{p\in\simplex : U = \Gamma(p)\}$.
\begin{lemma}
  If $L$ embeds $\ell$, then $L$ indirectly elicits $\gamma$.
\end{lemma}
\begin{proof}
  From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
  By definition of trim, for any $u\in\reals^d$, we have some $\theta \in \Theta$ such that $\Gamma_u \subseteq \theta$.
  Since $\trim(\gamma) = \Theta$, we have some $r\in\R$ such that $\theta = \gamma_r$, giving $\Gamma_u \subseteq \gamma_r$.
\end{proof}
\begin{lemma}
  Suppose $L$ indirectly elicits $\gamma$.
  If $\cap_{U\in\U'} U \neq \emptyset$ then $\cap_{U\in\U'} R_U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup_{U \ni u} \Gamma_U$.
  Suppose $\cap_{U\in\U'} U \neq \emptyset$, and let $u \in \cap_{U\in\U'} U$.
  As $u\in U$ for all $U\in\U'$, we have $\Gamma_U \subseteq \Gamma_u$ for all $U\in\U'$.
  By indirect elicitation, there exists some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  Thus, for all $U\in\U'$, we have $\Gamma_U \subseteq \gamma_r$ and thus $r\in R_U$.
  We conclude $\cap_{U\in\U'} R_U \neq \emptyset$.
\end{proof}

\raf{...END ALTERNATIVE}

The main problem now is to prove a ``thickened'' analogue of Lemma \ref{lem:calibrated-pos} that extends this link to points $u$ that are up to $\epsilon$ far from an optimal set $U$.
Namely, Lemma \ref{lem:thick-empty} will show that if $\epsilon$ is small enough, then the $\epsilon$-thickenings of all $U \in \U'$ intersect if and only if the $U$ sets themselves intersect.
Thus, if $u \in \cap_{U \in \U'} B(U,\epsilon)$, then $u \in \cap_{U \in \U'} U$, and Lemma \ref{lem:calibrated-pos} gives some legal target report $\psi(u) = r \in \cap_{U \in \U'} R_U$.

The next few geometric results build to Lemma \ref{lem:thick-empty}.
Then, the main proof will be completed as we have just sketched.

@@

\begin{corollary} \label{cor:thick-intersect}
  There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
\end{corollary}
\begin{proof}
  For each subset, Lemma \ref{lem:thick-empty} gives an $\epsilon_0 > 0$.
  We take the minimum over these finitely many subsets of $\U$.
\end{proof}

\begin{theorem} \label{thm:small-eps-thick}
  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ (Construction \ref{const:eps-thick-link}) is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
\end{theorem}
\begin{proof}
  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
  Consider any $u \in \R'$.
  If $u$ is not in $B(U,\epsilon)$ for any $U \in \U$, then we have $\Psi(u) = \R$, so it is nonempty.
  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
  By Lemma \ref{lem:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
\end{proof}

Theorem \ref{thm:thickened-separated}, which we restate here, is now almost immediate.
\thickenedseparated*
%% Bo: copying the text in a comment here for reference
%\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
%  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
%  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} yields an $\epsilon$-separated link with respect to $L$ and $\ell$.
%\end{restatable}
\begin{proof}
  We create $\psi$ using Construction \ref{const:eps-thick-link} with the $L_{\infty}$ norm.
  By Theorem \ref{thm:small-eps-thick}, for all small enough $\epsilon$, $\psi$ is well-defined everywhere.

  To prove separation, suppose $u$ and $p$ are given such that $d_{\infty}(u,U) \leq \epsilon$, where $U = \Gamma(p)$.
  Then in Construction \ref{const:eps-thick-link}, $\psi(u) \in \Psi(u) \subseteq R_U = \{r : \varphi(r) \in U\}$.
  By definition of embedding, $\varphi(r) \in U = \Gamma(p) \implies r \in \gamma(p)$.
  So we obtain $\psi(u) \in \gamma(p)$ whenever $d_{\infty}(u,\Gamma(p)) \leq \epsilon$, which proves $\epsilon$-separation of the link $\psi$.
\end{proof}

>>>>

\begin{definition}[Separated Link]\label{def:sep-link}
  Let properties $\Gamma:\simplex\toto\reals^d$ and $\gamma:\simplex\toto\R$ be given.
  We say a link $\psi:\reals^d\to\R$
  is \emph{$\epsilon$-separated with respect to $\Gamma$ and $\gamma$} if for all $u\in\reals^d$, $p\in\simplex$ with $\psi(u)\notin\gamma(p)$, we have $d_\infty(u,\Gamma(p)) \geq \epsilon$, where $d_\infty(u,A) \doteq \inf_{a\in A} \|u-a\|_\infty$.%
  \footnote{\citet{frongillo2021surrogate} define $\epsilon$-separation with a strict inequality $d_\infty(u,\Gamma(p)) > \epsilon$; we adopt a weak inequality as it is more natural in applications, such as hinge loss for binary classification.}
  Similarly, we say $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ if it is $\epsilon$-separated with respect to $\prop{L}$ and $\prop{\ell}$.
\end{definition}

@@

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{equation}
  \label{eq:intersection-property-embedding}
  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_u \neq \emptyset~.
\end{equation}
\noindent
Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points, and $\epsilon$-separated.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Let $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and embeds $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc\subseteq\R$.
  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
  For all $U \in \U$, define $R_U = \{r \in \Sc \mid \varphi(r) \in U\}$.
  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}
In \S~\ref{sec:poly-ie-consistency} we generalize this construction beyond embeddings, where we only require that $L$ indirectly elicits $\prop\ell$.
There we will see that, perhaps surprisingly, this construction recovers every possible calibrated link.

@@

We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
In particular, fast convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  \label{thm:linear-regret-bound}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
\end{theorem}
In the proof (\S~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
This expression gives the intuition that larger link separation is generally better for performance.
In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.

@@

\begin{construction}[general $\epsilon$-thickened link] \label{const:general-eps-thick-link}
  Let $L:\reals^d\to\reals^\Y_+$, $\gamma:\simplex\toto\R$, $\epsilon > 0$, and a norm $\|\cdot\|$ be given, such that $L$ is polyhedral and indirectly elicits $\gamma$.
  Define $\Gamma = \prop L$ and $\U = \{\Gamma(p) \mid p \in \simplex\}$.
  For all $U \in \U$, define $R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$, where $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$.
  The \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\R}$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}

@@

\section{Existence of a Separated Link} \label{app:sep-link-exists}
In this section, we prove Theorem \ref{thm:thickened-separated}, as discussed at the beginning of Appendix \ref{sec:equiv-sep-calib}: embeddings give rise to separated links.
We will prove this statement by combining three broader facts: (i) an embedding is a special case of indirect elicitation (Lemma~\ref{lem:embedding-implies-indirect-elic}), (ii) indirect elicitation is equivalent to eq.~\eqref{eq:intersection-property-embedding}, the intersection condition on optimal sets (Lemma~\ref{lem:intersection-equiv-indirect-elic}), and (iii) for polyhedral surrogates, this intersection condition implies separation (Proposition.......).
Combining these statements together will show that Construction~\ref{const:general-eps-thick-link}, a generalization of Construction~\ref{const:eps-thick-link}, gives a separated link.

\subsection{Indirect elicitation and optimal set intersection}

We first show (i), that embedding is a special case of indirect elicitation.
\begin{lemma}\label{lem:embedding-implies-indirect-elic}
  If $L$ embeds $\ell$, then $L$ indirectly elicits $\prop\ell$.
\end{lemma}
\begin{proof}
  Let $\Gamma = \prop L$ and $\gamma = \prop\ell$.
  From Proposition \ref{prop:embed-trim}, we have $\trim(\gamma) = \trim(\Gamma) =: \Theta$.
  By definition of trim, for any $u\in\reals^d$, we have some $\theta \in \Theta$ such that $\Gamma_u \subseteq \theta$.
  Since $\trim(\gamma) = \Theta$, we have some $r\in\R$ such that $\theta = \gamma_r$, giving $\Gamma_u \subseteq \gamma_r$.
\end{proof}

We next show (ii), the equivalence of indirect elicitation and the following intersection condition.

\begin{lemma}\label{lem:intersection-equiv-indirect-elic}
  Let $L:\reals^d\to\reals^\Y_+$ be polyhedral and $\gamma:\simplex\toto\R$ be a finite property.
  Define
  \begin{itemize}
  \item $\Gamma = \prop L$,
  \item $\U = \{\Gamma(p) \mid p \in \simplex\}$,
  \item $\Gamma_U := \{p\in\simplex \mid U = \Gamma(p)\}$ for all $U \in \U$,
  \item $R_U := \{r\in\R \mid \Gamma_U \subseteq \gamma_r\}$ for all $U \in \U$.
  \end{itemize}
  Then $L$ indirectly elicits $\gamma$
  if and only if the following condition holds
  \begin{align}
    \label{eq:general-intersection-condition}
    \forall \U'\subseteq\U,\; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
  \end{align}
\end{lemma}
\begin{proof}
  First assume $L$ indirectly elicits $\gamma$.
  Observe that, as $\U$ is the range of $\Gamma$, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U \mid U\in\U, u\in U\}$.
  Suppose $\cap_{U\in\U'} U \neq \emptyset$; let $u \in \cap_{U\in\U'} U$.
  As $u\in U$ for all $U\in\U'$, we have $\Gamma_U \subseteq \Gamma_u$ for all $U\in\U'$.
  By indirect elicitation, there exists some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  Thus, for all $U\in\U'$, we have $\Gamma_U \subseteq \gamma_r$ and thus $r\in R_U$.
  We conclude $\cap_{U\in\U'} R_U \neq \emptyset$.

  For the converse, let $u\in\reals^d$.
  If $\Gamma_u = \emptyset$, then $\Gamma_u \subseteq \gamma_r$ for any $r\in\R$.
  Otherwise, $\Gamma_u \neq \emptyset$, and the set $\U'_u = \{U\in\U \mid u\in U\}$ is nonempty.
  Moreover, $\cap \U'_u \neq \emptyset$ as $u\in\cap \U'_u$.
  Eq.~\eqref{eq:general-intersection-condition} now gives some $r\in\cap\{R_U \mid U\in\U'_u\}$.
  By definition of $R_U$, for all $U\in\U'_u$ we have $\Gamma_U \emptyset \gamma_r$.
  Thus $\Gamma_u = \cup\{\Gamma_U \mid U\in\U'_u\} \subseteq \gamma_r$, showing indirect elicitation.
\end{proof}

\subsection{Convex geometry for separation}

Let some norm $\|\cdot\|$ on $\reals^d$ be given.
Given a set $T\subseteq\reals^d$ and a point $u\in\reals^d$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.
Given two sets $T,T'\subseteq\reals^d$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.
Finally, for $T\subseteq \reals^d$ and $\epsilon > 0$, let the ``thickening'' $B(T,\epsilon)$ be defined as
\[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]

The goal of this subsection is to prove the first part of step (iii): for small enough $\epsilon>0$, if any set of $\epsilon$-thickened optimal sets intersect, then the optimal sets themselves must intersect.
We will conclude that, for small enough $\epsilon$, the link envelope $\Psi$ is non-empty everywhere, meaning there will be legal choices left over for the link.
\begin{lemma}~\label{lem:thick-intersect}
  Let $\U$ be defined as in Lemma~\ref{lem:intersection-equiv-indirect-elic}.
  There exists $\epsilon_0 > 0$ such that, for any $0 < \epsilon \leq \epsilon_0$, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\U$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
\end{lemma}

The next few geometric results build to Lemma~\ref{lem:thick-intersect}.

@@

The proof of Lemma~\ref{lem:thick-intersect} now follows: for each $\U'\subseteq\U$, Lemma \ref{lem:thick-empty} gives an $\epsilon_0(\U') > 0$; we take the minimum of $\epsilon_0(\U')$ over the finitely many choices of $\U'$.

\subsection{Separation for embeddings and beyond}

\begin{proposition}\label{prop:link-converse}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_\infty$.
  Then a link $\psi:\reals^d\to\R$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  Let $\U'_u = \{U\in\U \mid d_{\infty}(u,U) < \epsilon\}$.
  Then we have the following chain of equivalences.  
  % For any $u\in\reals^d$, we have $\psi(u)\in\Psi(u)$ if and only if $\psi(u) \in R_U$ for all $U\in\U'_u$, which is in turn equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $U\in\U'_u$.
  % Moreover, $\psi$ is $\epsilon$-separated if and only if we have $\psi(u)\in\gamma(p)$ for all $u\in\reals^d$ and $p\in\simplex$ with $d(u,\Gamma(p))<\epsilon$, which is equivalent to $\Gamma_U \subseteq \gamma_{\psi(u)}$ for all $u\in\reals^d$ and $U\in\U'_u$.
  \begin{align*}
    &\phantom{\iff}~\forall u\in\reals^d,\;\; \psi(u)\in\Psi(u)
    \\
    &\iff \forall u\in\reals^d,\, U\in\U'_u,\;\; \psi(u)\in R_U
    \\
    &\iff \forall u\in\reals^d,\, U\in\U'_u,\;\; \Gamma_U \subseteq \gamma_{\psi(u)}
    \\
    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } \Gamma(p)\in\U'_u,\;\; p \in \gamma_{\psi(u)}
    \\
    &\iff \forall u\in\reals^d,\, p\in\simplex \text{ s.t. } d(u,\Gamma(p)) < \epsilon,\;\; \psi(u) \in \gamma(p)
    \\
    &\iff \text{$\psi$ is $\epsilon$-separated}~.
      \qedhere
  \end{align*}
\end{proof}

From the equivalence of calibration and separation (Theorem~\ref{thm:calibrated-separated}), we now have the following.
\begin{corollary}\label{cor:link-char}
  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:general-eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|_{\infty}$.
\end{corollary}
